---
title: "Assignment0 - SRT411"
author: "Thomas Reid Zuk"
date: '2016-01-28'
output: 
  md_document:
    variant:  markdown_github

  
---


#### TODO #1
```{r}
((2014-2014)/(2014-1991))*100
```


#### TODO #2
```{r}
startDiff = 2014 - 2014
birthDiff = 2014 - 1991

decPer = startDiff/birthDiff

per = decPer * 100 
per
```

#### TODO #3
```{r}
nums = c(4,5,8,11)
sum(nums)
```

#### TODO #4
```{r, echo = FALSE}
plot(rnorm(100))
```

#### TODO #5
```{r}
help (sqrt)
```

Exert from sqrt Help:

Description

abs(x) computes the absolute value of x, sqrt(x) computes the (principal) square root of x, square root of {x}


#### TODO #6
```{r}
for(i in 1:4){
  source("src/firstScript.R")
}
```

#### TODO #7
```{r}
P = seq(from=31, to=60, by=1)
Q = matrix(data=P, ncol=5)
P
Q
```

#### TODO #8
```{r}
source("src/secondScript.R")
```


#### TODO #9
```{r}
source("src/secondScriptV2.R")
```

+ rgb is a function that sets colour based on RGB values and transparency based on alpha 

+ lwd is the line width, default value of 1 if not specified

+ pch a integer or character that draws a sequence of points at the specified coordinates

+ cex number value that specifies the magnification (size) or elements like text or symbols



#### TODO #10
```{r}
data = read.table(file="src/tst1.txt", header=TRUE)
newData = data$g*5
write.table(newData, file="src/tst2.txt", row.names=FALSE)
read.table(file="src/tst2.txt")
```

#### TODO #11
```{r}
vec = c(rnorm(100))
mean(sqrt(vec))
```
+ NaN's produced because the square root of a negative integer is an imaginary number,which for the purpose of this demonstration and simplicity does not exist.


#### TODO #12
```{r}
dates = strptime(c("20160123", "20161225", "20161206"), format="%Y%m%d")
pres = c(1,8,10)
plot(dates,pres, xlab="Dates", ylab="Expected Presents")
```

#### TODO #13
```{r}
loopVec = seq(1:100)
newVec = c()
for(i in loopVec){
  if(i<5 || i>90){
    newVec[i]=loopVec[i]*10
  }else{
    newVec[i]=loopVec[i]*0.1
  }
}
print(newVec)
```


#### TODO #14
```{r}
func1 = function(arg1){
  resVec = c()
  for(i in 1:length(arg1)){
    if(i<5 || i>90){
      resVec[i]=arg1[i]*10
    }else{
      resVec[i]=arg1[i]*0.1
    }
  }
  return(resVec)
}

vec14a = c(0,1,2,3,5,10,25,30,99,150)
func1(vec14a)
```


#### TODO #15/Footnote challenge
+ The following code displays the time it takes to execute a vector computation versus the time it takes a for-loop to perform the same work
```{r}
vect1 = c(-2,-3,-1,0,1,2,3,5,5,7,10,25,30,50,70,80,99,101,110,150,200)

func2 = function(arg1){
  result <- ifelse(arg1 < 5 | arg1 > 90, arg1 * 10, arg1 * 0.1)
  return(result)
}
vect2 = func2(vect1)
```
+ Time take using vector computation, non-loop
```{r}
system.time(replicate(10000, func2(vect1)))
```
+ Time take using for-loop
```{r}
vec15a = c(0,1,2,3,5,10,25,30,99,150)
system.time(replicate(10000, func1(vec15a)))

```



### Sources:

https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf

http://kbroman.org/knitr_knutshell/pages/markdown.html

https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf

http://www.r-bloggers.com/using-apply-sapply-lapply-in-r/

https://www.rstudio.com/

https://cran.r-project.org/

https://github.com/swirldev/swirl

http://stackoverflow.com/questions/tagged/r
